---
title: "Comparison class inference via syntactic cues"
author: "Polina Tsvilodub"
date: "25 09 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE )
```

``` {r}
library(tidyboot)
library(tidyverse)
library(lmerTest)
# library(emmeans)
library(brms)
```
# Hypothesis Outline

Syntactic cues like the position of the noun phrase in a sentence might help listeners restrict the possible comparison classes upon hearing a sentence with a gradable adjective like "That great dane is big". We test this hypothesis in three experiments manipulating the syntax of a sentence that is used to describe an object: the syntax is either "That NP is big (small)" (predicative condition) or "That's a big (small) NP" (prenominal condition). 
__We hypothesis that NPs in the prenominal condition restrict the comparison class and thus, given our experimental design, this syntax is felicitous with a basic-level label of the target object but not with a subordinate label. In contrast, in the predicative condition the comparison class is less restricted, and thus using both the basic-level and the subordinate label of the target as the NP is felicitous.__
Here, both Bayesian and frequentist analyses of the experimental data are presented.  

## Syntax Rating Experiment
The goal of the experiment was to obtain ratings of both syntactic conditions in direct comparison as descriptions of a target referent in context. The context picture was followed by a sentence providing the subordinate level label of the traget. Below the sentence, the picture of the target appeared and they were asked: "How well does each of the sentences describe it?"
__Between-subject:__ order of the syntactic frames on the sliders
__Within-subject:__ NP (basic-level or subordinate level), target size (big or small), congruence (big great dane or small great dane)
__Expectation:__ In the congruent condition, given sentences with subordinate noun phrases (e. g. great dane), we expect higher mean ratings of the Subject than the Predicate condition. Sentences with basic-level noun phrases should elicit similarly high ratings, regardless of syntactic condition. In the incongruent condition, the prenominal subordinate condition is expected to elicit the highest rating, since it is the only sentence felicitous to describe the target. The endorsement wwill probably be lower than in the congruent condition. Predicative subordinate and both basic-level conditions are expected to elicit the lowest ratings. 

### Mean rating in different conditions 
n = 30 (1 excluded as non-native speaker)
```{r syntax rating, echo = FALSE}
d_rating <- read_csv("./data/results_14_syntax-rating_30.csv")
d_rating_filter <- d_rating %>% filter(grepl("en", languages, ignore.case = T))
d_rating_warmup <- d_rating_filter %>% filter(trial_name == "custom_warmup")
d_rating_main <- d_rating_filter %>% filter((trial_name == "custom_slider1") | (trial_name == "custom_slider2"))

d_rating_main <- d_rating_main %>% mutate(np = factor(np, levels= c(0,1), 
                                                      labels = c("sub", "super")), 
                 sentence_order = factor(sentence_order, levels= c("0|1", "1|0"),
                                         labels = c("prenom_pred", "pred_prenom")),
                 target_size = factor(target_size, levels = c(0,1), 
                                      labels = c("big", "small")),
                 congruence = factor(congruence, levels = c(0, 1), 
                                     labels = c("congr", "incongr")))

# sort responses (due to bad recoding)
d_main_pred_prenom_pred <- d_rating_main %>% filter(sentence_order == "pred_prenom")  %>%
  select(submission_id, np, congruence, response1, target_size, trial_number, item) %>% mutate(condition = "pred")
d_main_pred_prenom_prenom <- d_rating_main %>% filter(sentence_order == "pred_prenom") %>%
  select(submission_id, np, congruence, response1 = response2, target_size, trial_number, item) %>% 
  mutate(condition = "prenom")
d_main_prenom_pred_prenom <- d_rating_main %>% filter(sentence_order == "prenom_pred") %>%
  select(submission_id, np, congruence, response1, target_size, trial_number, item) %>% mutate(condition = "prenom")
d_main_prenom_pred_pred <- d_rating_main %>% filter(sentence_order == "prenom_pred") %>%
  select(submission_id, np, congruence, response1 = response2, target_size, trial_number, item) %>% 
  mutate(condition = "pred")

# subset data frames
rating_prenom <- rbind(d_main_pred_prenom_prenom, d_main_prenom_pred_prenom)
rating_pred <- rbind(d_main_pred_prenom_pred, d_main_prenom_pred_pred)
d_rating_full <- rbind(rating_pred, rating_prenom)  %>%   mutate(condition = factor(condition, 
                            levels = c("pred", "prenom"), 
                            labels = c("subject", "predicate")),
         congruence = factor(congruence, levels = c("congr", "incongr"), 
                             labels = c("congruent\n ('big' great dane)", "incongruent\n ('small' great dane)")),
         np = factor(np, levels = c("super", "sub"), labels = c("basic/superordinate", "subordinate"))) 


# plot 
bar.width = 0.8

d_rating_full %>%
  group_by(np, congruence, condition) %>% 
  tidyboot_mean(column = response1) %>% 
  ggplot(aes(x = condition, y = mean, fill = np, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(bar.width), width = bar.width, alpha = 0.3, color = 'black') +
  geom_point(data = d_rating_full, 
             position = position_jitterdodge(),
             inherit.aes = F, aes(x = condition, y = response1, color = np),
             alpha = 0.25)+
  geom_linerange(position = position_dodge(bar.width))+ 
  facet_wrap(~congruence) +
  xlab("NP position") + 
  ylab("mean sentence rating") +
  ggtitle("Mean ratings by syntactic condition and congruence")
```

### Stats

Prediction: 

Basic - Subordinate (looks like this could positive, but we predict it should not be significant)
Subject - Predicate (looks like this could positive, but we predict it should not be significant)

Basic - Subordinate
x
Subject - Predicate
--> beta < 0


``` {r rating lmer stats 2-way}
# contrast coding of the variables, creating numeric variables
# NP: 1 sub, -1 super (basic)
# congruence:1 congruent, -1 incongruent
# condition: 1 predicative, -1 prenominal
d_rating_full <- d_rating_full %>% mutate(np = C(factor(np), sum),
                                          congruence = C(factor(congruence), sum),
                                          condition = C(factor(condition), sum))
contrasts(d_rating_full$np)
contrasts(d_rating_full$condition)


lm.fit <- lmer(response1 ~ condition * np + 
                  #(1 | submission_id) + 
                  #(1 | item) +
                  #(0 + np | submission_id) + 
                  #(0 + np | item) +
                  #(0 + condition | submission_id) + 
                  #(0 + condition | item) +
                  #(0 + condition:np | submission_id),# + 
                  (0 + condition:np | item), 
               data = d_rating_full %>%
                 filter(congruence == "congruent\n ('big' great dane)"), 
               REML = F)

summary(lm.fit)
```


```{r}
lm.fit.2 <- lmer(response1 ~ condition * np + 
                  #(1 | submission_id) + 
                  #(1 | item) +
                  #(0 + np | submission_id) + 
                  #(0 + np | item) +
                  #(0 + condition | submission_id) + 
                  #(0 + condition | item) +
                  (0 + condition:np | submission_id),# + 
                  #(0 + condition:np | item), 
               data = d_rating_full %>%
                 filter(congruence == "incongruent\n ('small' great dane)"), 
               REML = F)

summary(lm.fit.2)
```


This is a linear model of the rating predicted by the syntactic condition, the noun phrase, the congruence and their interaction with random intercept by-participant and random intercept by-item effects.


```{r rating lmer stats 3-way}
# linear model
lm.fit <- glmer(response1 ~ condition * np * congruence + 
                  (1 + condition*np*congruence || submission_id) + 
                  (1 + condition*np*congruence || item), data = d_rating_full, REML = F)
summary(lm.fit)

#confint(lm.fit)
```

### Bayesian Stats
``` {r rating bayes stats, echo=FALSE}
#b.lm.fit <- brm(response1 ~ condition * np * congruence + (1 | submission_id) + (1 | item), data = d_rating_full)
#summary(b.lm.fit)
```


## NP Free Production Experiment 

In this experiment we want to see if speakers actually use different labels as noun phrases to describe the target, given different syntactic frames. The participants saw a basic-level context, below the sentence "This one is also in the parade", referring to the target. The target picture (big or small, balanced within-subject) was followed by the prompt "You say to your friend: ". Participants see either "That's a big (small) __ " or "That __ is big (small)" (between-subjects), blank to be filed in. The target size and adjective were always 'congruent'.
__Expectation:__ We expect a higher proportion of subordinate target labels in the predicative than in the prenominal conidtion.

### Proportions of subordinate responses by syntactic condition
n = 120 (n = 58 prenominal syntax, n = 60 predicative syntax)
``` {r production, echo = FALSE}
d1 <- read_csv('./data/results_8_exp1-post-prereg-pred.csv')
d2 <- read_csv('./data/results_10_exp1-post-prereg-prenom.csv')
d3 <- read_csv('./data/results_8_exp1-post-prereg-pred_batch2.csv')
d4 <- read_csv('./data/results_10_exp1-post-prereg-prenom_batch2.csv')
x <- rbind(d1, d3)
y <- rbind(d2, d4)
d_prod <- rbind(x, y)

d_prod_filt <- d_prod %>% 
  filter(grepl("eng", languages, ignore.case = T)) %>%
  select(submission_id, trial_name, trial_number, size, item, botresponse, response,
         condition,  picture) %>% mutate(size=factor(size), syntax = factor(condition))

d_prod_main <- d_prod_filt %>% filter((trial_name =="main1") | (trial_name== "main2")) %>%
  select(submission_id, trial_number, response,  size, item, syntax, condition, picture)

d_prod_main_valid <- subset(d_prod_main, !(response %in% c("rose", "duck", "weed", "pigeon", "stingfish", "rat"))) 

d_prod_main_responseCat <- d_prod_main_valid %>%
  rowwise() %>%
  mutate( # categorize responses 
    response_cat =
      ifelse(
      tolower(response) %in% c("bird", "birds", "dog", "dogs", "fish","one plant",
                               "flower", "flowers", "tree", "trees", "animal", "plant"),
      "super", "sub"),
    resp_cat = ifelse(response_cat == "sub", 1, 0),
    response_label = "sub"
  )

# plot
d_prod_main_responseCat %>%
  group_by(syntax, response_label) %>%
  tidyboot_mean(column = resp_cat) %>% # calculate proportion of subordinate labels in the different conditions 
  ungroup() %>%
  mutate(syntax = factor(syntax, 
                            levels = c("prenominal", "predicative"),
                            labels= c("That's a big X", "That X is big"))
        ) %>% 
  ggplot(aes(x = syntax, fill = syntax,
                           y = mean, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(0.8)) +
  geom_linerange(position = position_dodge(0.8)) +
  labs( y = "Proportion subordinate responses") +
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
  ggtitle("The proportion of subordinate responses by syntactic condition")

```

### Stats
The reponse category (subordinate vs basic-level) is regressed against the syntax and random intercept by-participant and random intercept and syntax-effects by-item. The syntax is contrast coded, predicative syntax being the reference level. 

``` {r production lmer}

# predicative syntax is reference level (-1)
contrasts(d_prod_main_responseCat$syntax)=matrix(c(-1, 1))
# fit regression model
prod.lm.fit <- glmer(resp_cat ~  syntax + (1 + syntax| submission_id) + (1 + syntax|picture), data = d_prod_main_responseCat, family="binomial", REML = F)
summary(prod.lm.fit)
#confint(prod.lm.fit)
```


### Bayesian Stats

``` {r production bayes, echo = FALSE}
#contrasts(d_prod_main_responseCat$syntax)=matrix(c(-1, 1))

#get_prior(resp_cat ~ 0 + syntax + (1| submission_id) + (1 + syntax|picture),
 #         data=d_prod_main_responseCat, family= "bernoulli")
# uniform prior 
#Prior <- set_prior("beta(1,1)", class = "b", lb = 0, ub = 1)
#b.lm.w_prior <- brm(resp_cat ~   0 + syntax + (1| submission_id) + (1 + syntax|picture), 
 #                 data = d_prod_main_responseCat, family = "bernoulli",
  #                prior = Prior, sample_prior = T)

#summary(b.lm.w_prior)
# nullhypothesis that proportions do not differ
#h1_1 <- hypothesis(b.lm.w_prior, "0 - syntaxpredicative = 0 + syntaxprenominal") 

#print(h1_1, digits = 3)
# probability of alternative hypothesis given the data 
#1/h1_1$hypothesis$Evid.Ratio
```

## Comparison Class Inference Experiment

The question in this experiment is whether participants' comparison class inference is influenced by the syntactic frame. Participants are asked to paraphrase a sentence in a free production task: They see the context (basic-level or subordinate, balanced within-subject) and are told that they and a friend see another not pictured member of the group. Their friend utters a sentence (one of the two syntactic frames, between-subject), after which the question "What do you think your friend meant?" is presented. The NP of the uttered sentence is either unerspecified ('one') or the subordinate target label (balnced within-subject). The paraphrase template is "It is big (small) relative to other __ ", blank to be filled in. There are congruent and incongruent trials in the basic-level context. 
__Expectation:__ In the underspecified NP condition ('one'), we expect the perceptual context to set the comparison class, i. e. subordinate paraphrase in subordinate contexts and basic-level paraphrase in basic-level contexts in both congruent and incongruent trials. In the subordinate NP condition, in the congruent condition ('big' with a priori big targets) we expect a syntax effect: The prenominal syntax should elicit less basic-level paraphrases than the predicative syntax.

### Proportion of basic-level responses by congruence and NP condition
n = 50 (n = 25 in prenominal, n = 25 in predicative condition)
Superordinate labels are collapsed with the basic labels 
```{r inference, echo = FALSE}
d1_infer <- read_csv("./data/results_12_comp-class-infer-pred.csv")
d2_infer <- read_csv("./data/results_13_comp-class-infer-prenom.csv")
d_infer <- rbind(d1_infer, d2_infer)

d_infer <- mutate(d_infer, NP = factor(ref_spec, levels= c(0, 1), 
                                       labels = c("subordinate", '"one"')), 
                  context_adj = factor(pic_spec, levels = c(0, 1, 2), 
                                       labels = c("congruent\n basic-level parade", 
                                                  "congruent\n subordinate parade",
                                                  "incongruent\n subordinate parade")))
d_infer_filt <- d_infer %>% 
  filter(grepl("en", languages, ignore.case = T))
# choose main trials 
d_infer_main <- d_infer_filt %>% filter((trial_name == "custom_main_text1")|
                                          (trial_name == "custom_main_text2")) %>%
  select(submission_id, trial_number, NP, context, context_adj, item, response, condition,
         context_picture, adj_cond, target_size)

d_infer_main_responseCat <- d_infer_main %>%
  rowwise() %>%
  mutate(  
    response_cat =
      ifelse(
        tolower(response) %in% c("birds", "dogs", "fish", "fishes", "flowers", 
                                 "flower", "large dogs", "dogs in the line",
                                 "other birds in the group", "small dogs", "trees",
                                 "tree's", "bird", "big tree"), "basic", 
        ifelse(tolower(response) %in% c("plant", "animal", "things", "weeds", "plants"),
               "super", "sub")),
    
    response_num = ifelse(response_cat == "sub", 0, 1),
    response_label = "basic"
  )

# include a context condition column
d_infer_main_responseCat <- d_infer_main_responseCat %>% rowwise() %>%
  mutate(
    context_cond = ifelse(context_adj == "congruent dog parade", "basic", "sub" )
  )

d_infer_main_responseCat$condition <- factor(d_infer_main_responseCat$condition, 
                                             levels = c("prenominal", "predicative"))
bar.width = 0.8
d_infer_main_responseCat %>%  
  group_by(response_label, NP, context_adj, condition) %>%
  tidyboot_mean(column = response_num) %>% ungroup() %>% 
  mutate(condition = factor(condition, levels = c( "predicative", "prenominal"), 
                            labels = c( "Subject", "Predicate"))) %>%
  ggplot(aes(x=condition, y = mean, fill = NP, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(bar.width), width = bar.width) +
  geom_linerange(position = position_dodge(bar.width)) + 
  xlab("NP condition") +
  ylab("proportion of basic-level responses")+
  facet_grid(~context_adj)  

```

### Stats
The response category (basic collapsed with superordinate labels vs subordinate) is regressed against the syntactic condition (contrast coded), NP ('one' vs subordinate), the congruence + context condition (context_adj) , their interaction and random intercept by-participant and random intercept and syntax by-context-item (context conditions) effects. NB: model does not converge for separate context and congruence conditions.    
``` {r inference lmer}
# prenominal condition is reference level (-1)
d_infer_main_responseCat <- d_infer_main_responseCat %>% mutate(congruence = 
                                                                  ifelse(adj_cond == "incongr", "incongr", "congr"))
d_infer_main_responseCat$congruence <- factor(d_infer_main_responseCat$congruence, levels = c("congr", "incongr")) 
d_infer_main_responseCat$context_cond <- factor(d_infer_main_responseCat$context_cond, levels = c("sub", "basic")) 
# -1 prenominal, 1 predicative
contrasts(d_infer_main_responseCat$condition)=matrix(c(-1, 1))
# -1 subordinate, 1 one
contrasts(d_infer_main_responseCat$NP) = matrix(c(-1,1))
#-1 sub, 1 basic context picture
contrasts(d_infer_main_responseCat$context_cond) = matrix(c(-1,1))
# -1 congruent, 1 incongruent condition
contrasts(d_infer_main_responseCat$congruence) = matrix(c(-1,1))


lm.infer.fit <- glmer(response_num ~ condition*NP*congruence*context_cond  + 
                       (1 + condition*NP|| submission_id) + (1 + condition*NP || item), 
                data = d_infer_main_responseCat, family = "binomial" , REML = F)
summary(lm.infer.fit)

```

### Bayesian Stats
``` {r inference bayes, echo = FALSE}
#contrasts(d_infer_main_responseCat$condition)=matrix(c(-1, 1))
#b.lm.infer.fit <- brm(response_num ~ condition*NP*context_adj + 
 #                      (1|submission_id) + (1 + condition | item), 
  #              data = d_infer_main_responseCat, family = "binomial" )
#summary(b.lm.infer.fit)

```

### Stats including label frequency 
``` {r inference item frequency, echo = FALSE}
item_freqs <- read_csv('./comp-class-inference/data/item_freqs.csv') 
# include the pure basic level category string
d_infer_main_responseCat <- d_infer_main_responseCat %>% rowwise() %>% 
  mutate(basic_cat = ifelse(item == "dogs1", "dogs",
                            ifelse(item == "dogs2", "dogs", item)))
# include the subordinate level category string 
                                                                                         
return_item <- function(condition, context_pic, target_size) {
  if(condition == "incongr") {
    x = sub("images/.*-parade-", "", context_pic)
    x = sub(".png", "", x)
    x = sub("-", " ", x)
  } else if (condition == "congr") {
    x = sub("images/.*-parade-", "", context_pic)
    x = sub(".png", "", x)
    x = sub("-", " ", x)
  } else {
    if (context_pic == "images/bird-parade-basic.png") {
      if (target_size == "small") {
        x=  "hummingbird"
      } else {
        x= "eagle"
      }
    } else if (context_pic == "images/dog-parade-basic.png") {
      if (target_size == "small") {
        x= "chihuahua"
      } else {
        x= "doberman"
      }
    } else if (context_pic == "images/dog-parade-basic2.png") {
      if (target_size == "small") {
        x= "pug"
      } else {
        x= "great dane"
      }
    } else if (context_pic == "images/fish-parade-basic.png") {
      if (target_size == "small") {
        x= "goldfish"
      } else {
        x= "swordfish"
      }
    } else if (context_pic == "images/flower-parade-basic.png") {
      if (target_size == "small") {
        x= "dandelion"
      } else {
        x= "sunflower"
      }
    } else {
      if (target_size == "small") {
        x= "bonsai"
      } else{
        x= "redwood"
      }
    }
  }
  return(x) 
}
items_vec <- Vectorize(return_item, vectorize.args = c("condition", "context_pic", "target_size"))

exp_sub <- items_vec(d_infer_main_responseCat$adj_cond, d_infer_main_responseCat$context_picture, d_infer_main_responseCat$target_size)

d_infer_main_responseCat <- cbind(d_infer_main_responseCat, exp_sub)
d_infer_main_responseCat$sub_freq <- item_freqs$log_sub_log_basic[match(d_infer_main_responseCat$exp_sub, item_freqs$np)]
d_infer_main_responseCat$basic_freq <- log(item_freqs$np_freqs[match(d_infer_main_responseCat$basic_cat, item_freqs$np)])
```

``` {r inference item frequency lmer}
# lm with frequency effect

#lm.infer.freq.fit <- glmer(response_num ~ condition*NP*context_cond*congruence + 
 #                            sub_freq +
#                       (1 + condition*NP|| submission_id) + (1 + condition*NP || item), 
 #               data = d_infer_main_responseCat, family = "binomial", REML = F )
#summary(lm.infer.freq.fit)
```