---
title: "Double Modification Ref Utility with Fillers"
author: "Polina Tsvilodub"
date: "07 05 2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lmerTest)
library(brms)
library(tidyboot)
```


``` {r data, echo=FALSE, warnings=FALSE, include=FALSE}
#d_mod_filler <- read_csv('../data/results_35_modification-refUt-filler-pilot.csv')
#d_mod_filler_clean <- d_mod_filler %>% select(-worker_id, -hit_id, -startDate, -assignment_id)
#write_csv(d_mod_filler_clean, '../data/results_35_modXrefUt_pilot1.csv')
d_mod_ref <- read_csv('../data/results_35_modXrefUt_pilot1.csv')
```
## Data Exclusion

Four participants are excluded for not reporting their native language. One is excluded for failing labeling trials (mostly due to typos).
```{r clean}
# exclude participants who report glitches
d_mod_ref %>% select(submission_id, comments, problems) %>% distinct() %>% View()
d_modRef_woGlitches <- d_mod_ref 

# exclude non-native English speakers
d_modRef_woGlitches %>% distinct(languages) %>% View()

d_modRef_Native <- d_modRef_woGlitches %>% 
  filter(grepl("en", languages, ignore.case = T)) 

# cleaning warm-up trials
# comparison class paraphrase trial
d_failed_cc_warmup <- d_modRef_Native %>% 
  filter( trial_name == "comp_class_warmup") %>%
  group_by(submission_id) %>% count() %>%
  filter( n > 4 )
d_failed_label_warmup <- d_modRef_Native %>%
  filter( (trial_name == "warmup1") | (trial_name == "warmup2")) %>%
  group_by(submission_id) %>%
  filter(attempts > 4)
d_label_warmup_more1 <- d_modRef_Native %>%
  filter( (trial_name == "warmup1") | (trial_name == "warmup2")) %>%
  group_by(submission_id) %>%
  filter(attempts > 1) %>% ungroup() %>% 
  select(submission_id, picture1, response1, picture2, response2, attempts)
# check where and why people need more than one attempt 
# d_Native %>% 
#filter((trial_name == "warmup1") | (trial_name == "warmup2")) %>% #semi_join(., d_label_warmup_more1, by=c("submission_id")) %>% #select(submission_id, picture1, response1, picture2, response2, attempts) %>% View()
d_modRef_filter <- anti_join(d_modRef_Native, d_failed_cc_warmup, by = c("submission_id"))
d_modRef_filter <- anti_join(d_modRef_filter, d_failed_label_warmup, by = c("submission_id"))
```

The number of conditions we collected data for is relatively balanced. 
``` {r count}
d_modRef_filter %>% count(adj_cond, syntax)
d_modRef_filter %>% count(adj_cond, syntax, target_size)
d_modRef_filter %>% count(adj_cond, target, syntax)
```

## Response Classification

Data from n = 41 is classified into basic-level and subordinate responses. 9 (4 %) invalid responses where participants fail to establish correct reference or produce nonsense are excluded. 
``` {r}
d_modRef_main <- d_modRef_filter %>% filter((trial_name == "custom_main_text1") |
                                (trial_name == "custom_main_text2")) %>%
  select(submission_id, trial_number, context_picture, response, target_size, adj, syntax, target, item, adj_cond, trial_type )
```

``` {r}
d_modRef_main %>% distinct(response) %>% View()

d_modRef_excludeN2 <- d_modRef_main %>% 
  subset(., !(tolower(response) %in% c("prize-winner", "gifts", "rescues", "prizes",
                                       "landmarks", "prizewinners", "service animals", "prize winnders", "service dogs", "prize winners")))

(nrow(d_modRef_main) - nrow(d_modRef_excludeN2))/nrow(d_modRef_main)

d_modRef_valid <- d_modRef_excludeN2 %>% 
  subset(., !(tolower(response) %in% c("everything", "big", "human")))

d_modRef_main_responseCat <- d_modRef_valid %>% 
  mutate(response_cat = ifelse(
    tolower(response) %in% c("flowers", "flower", "trees", "tree",  "birds", "bird",  "dogs", "dog", "plants", "other trees" ), "basic", "subordinate"
  ),
  response_num = ifelse(response_cat == "basic", 1, 0)
  )
```

``` {r}
d_modRef_matchNP <- d_modRef_main %>%
  subset(., !(tolower(response) %in% c("everything", "big", "human"))) %>%
  mutate(
    NP_match = ifelse(
      tolower(response) %in% c("prize-winner", "gifts", "rescues", "prizes",
                          "landmarks", "prizewinners", "service animals", "prize winnders", "service dogs", "prize winners", "flowers", "flower", "trees", "tree",  "birds", "bird",  "dogs", "dog", "plants", "other trees"), "nonmatch", "match"
    ), 
    response_numMatch = ifelse(NP_match == "nonmatch", 1, 0)
  )
write_csv(d_modRef_matchNP, '../data/results_35_modXrefUt_pilot1_nonMatchClassified_tidy.csv')  
```

```{r plot, echo=FALSE}
bar.width = 0.8
d_modRef_main_responseCat %>%  
  group_by(syntax, trial_type) %>%
  tidyboot_mean(column = response_num) -> d_modRef_main_responseCat.bs

d_modRef_main_responseCat.bs %>%
  ungroup() %>%
  mutate(syntax = factor(syntax, levels = c("subj", "pred"), 
                         labels = c("Subject NP", "Predicate NP"))) %>%
  ggplot(., aes(x=syntax, y = mean, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(bar.width), width = bar.width, color= 'black',
           alpha = 0.5, color = 'black', size = 0.5) +
  geom_linerange(position = position_dodge(bar.width), size = 0.5) +
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  ylab("Proportion of basic-level responses") +
  facet_grid(~trial_type)
```

```{r plot, echo=FALSE}
bar.width = 0.8
d_modRef_matchNP %>%  
  group_by(syntax, trial_type) %>%
  tidyboot_mean(column = response_numMatch) -> d_modRef_match_responseCat.bs

d_modRef_match_responseCat.bs %>%
  ungroup() %>%
  #filter(trial_type == "critical") %>%
  mutate(syntax = factor(syntax, levels = c("subj", "pred"), 
                         labels = c("Subject NP", "Predicate NP"))) %>%
  ggplot(., aes(x=syntax, y = mean, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(bar.width), width = bar.width, color= 'black',
           alpha = 0.5, color = 'black', size = 0.5) +
  geom_linerange(position = position_dodge(bar.width), size = 0.5) +
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  ylab("Proportion of responses \nnot matching critical NP") +
  ggtitle('Direct Modification Pilot 5' ) +
  facet_grid(~trial_type)
ggsave('modificationXrefUt_by-trialType.png', height = 3, width = 5)
```

```{r by-item match, echo=FALSE}
bar.width = 0.8
d_modRef_matchNP %>%  
  group_by(syntax, target, trial_type) %>%
  tidyboot_mean(column = response_numMatch) -> d_modRef_match_responseCat.byItem

d_modRef_match_responseCat.byItem %>%
  ungroup() %>%
  #filter(trial_type == "critical") %>%
  mutate(syntax = factor(syntax, levels = c("subj", "pred"), 
                         labels = c("Subj NP", "Pred NP"))) %>%
  ggplot(., aes(x=syntax, y = mean, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(bar.width), width = bar.width, color= 'black',
           alpha = 0.5, color = 'black', size = 0.5) +
  geom_linerange(position = position_dodge(bar.width), size = 0.5) +
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  ylab("Proportion of responses \nnot matching critical NP") +
  ggtitle('Direct Modification Pilot 5' ) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        strip.text.y = element_text(angle = 90)) +
  facet_grid(trial_type~target, scales = "free")
ggsave('modificationXrefUt_by-ItemXTrial.png', height = 3, width = 9)
```

``` {r}

d_modRef_matchNP %>%  
  group_by(syntax, submission_id, trial_type) %>%
  tidyboot_mean(column = response_numMatch) %>%
  ungroup() %>%
  #filter(trial_type == "critical") %>%
  mutate(syntax = factor(syntax, levels = c("subj", "pred"), 
                         labels = c("Subj NP", "Pred NP"))) %>%
  ggplot(., aes(x=syntax, y = mean, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(bar.width), width = bar.width, color= 'black',
           alpha = 0.5, color = 'black', size = 0.5) +
  geom_linerange(position = position_dodge(bar.width), size = 0.5) +
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  ylab("Proportion of responses \nnot matching critical NP") +
  ggtitle('Direct Modification Pilot 5' ) +
  theme(strip.text = element_text(size=5),
        strip.background = element_rect(size = 1)) +
  facet_wrap(submission_id~trial_type, ncol=8, scales = "free")
ggsave('modificationXrefUt_by-SubjXTrial.png', height = 5, width = 8)

```

### stats
``` {r}
d_modRef_matchNP %>%
  mutate(syntax_dev = ifelse(syntax == "subj", 1, -1)) %>%
  filter(trial_type == "critical") -> d_modRef_critical
d.mod.refUt.brm <- brm(
  response_numMatch ~ syntax_dev + (1 + syntax_dev | submission_id) +
    (1 + syntax_dev | target),
  data = d_modRef_critical,
  family = "bernoulli",
  cores = 4,
  control=list(adapt_delta=0.95)
)
summary(d.mod.refUt.brm)
```