---
title: "Modification Manipulation Pilots 1-3 Exploratory Analyses"
author: "Polina Tsvilodub"
date: "09 04 2020"
output: github_document
---

For an exploratory analysis, the categorized data from all three noun modification manipulation pilots is pooled. 

``` {r libraries, echo=F, warnings=F, include=F}

library(tidyverse)
library(tidyboot)
library(brms)
library(lmerTest)
```

``` {r echo=F, warnings=F, include=F}
pilot1 <- read_csv('../data/results_32_modification_manipulation_pilot1_tidy.csv')
pilot2 <- read_csv('../data/results_32_modification_manipulation_pilot2_tidy.csv')
pilot3 <- read_csv('../data/results_32_modification_manipulation_pilot3_tidy.csv')

all_pilots <- rbind(pilot1, pilot2, pilot3)
```

``` {r}
bar.width = 0.8

all_pilots %>%
  group_by(syntax) %>%
  tidyboot_mean(column = response_num) -> all_pilots.bs


all_pilots.bs %>%
  ungroup() %>%
  mutate(syntax = factor(syntax, levels = c( "subject", "predicate"),
                            labels = c(  "Subject NP\n(That big NP is a prize-winner)", "Predicate NP\n(That prize-winner is a big NP)"))) %>%
  ggplot(., aes(x=syntax, y = mean, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(bar.width), width = bar.width, color= 'black',
           alpha = 0.5, color = 'black', size = 0.5) +
  geom_linerange(position = position_dodge(bar.width), size = 0.5) +
  ggthemes::theme_few()+
  xlab("") +
  theme(legend.position = c(0.88, 0.84),
        legend.key.size = unit(0.5,"line"))+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  ylab("Proportion of basic-level responses")
  
```

``` {r}
all_pilots %>%  
  group_by(syntax, item, adj) %>%
  tidyboot_mean(column = response_num) -> all_pilots.bs.item


all_pilots.bs.item %>%
  ungroup() %>%
  mutate(syntax = factor(syntax, levels = c( "subject", "predicate"),
                            labels = c(  "Subject NP\n(That big NP\n is a prize-winner)", 
                                         "Predicate NP\n(That prize-winner\n is a big NP)")),
         size = factor(adj, level = c("big", "small"), labels = c("big", "small"))) %>%
  ggplot(., aes(x=syntax, y = mean, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(bar.width), width = bar.width, color= 'black',
           alpha = 0.5, color = 'black', size = 0.5) +
  geom_linerange(position = position_dodge(bar.width), size = 0.5) +
  ggthemes::theme_few()+
  xlab("") +
  theme(legend.position = c(0.88, 0.84),#legend.text = element_text(size = 7),
        #legend.title = element_text(size = 7), 
        legend.key.size = unit(0.5,"line"))+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  ylab("Proportion of basic-level responses") +
  ggtitle("By-item inferred Comparison Classes")+
  facet_grid(item~size)

```
A Bayesian model with random by-item and by-subject intercepts and random syntax slope-effects and fixed effects of syntax (deviation coded) and experiment (dummy-coded):
``` {r}
all_pilots <- all_pilots %>%
  mutate(pilot_nr = factor(pilot_nr))

d.infer.full.brm <- brm(response_num ~ syntax_dev + pilot_nr + 
                          (1 + syntax_dev | submission_id ) + 
                          (1 + syntax_dev | target ),
                   data = all_pilots,
                   family = "bernoulli",
                   cores = 4,
                   control = list(adapt_delta = 0.99))

summary(d.infer.full.brm)
```
## Pilots 1 - 5
In this section, data from 5 pilots is pooled. To do so, only the congruent condition data is subsetted from the fourth pilot; and only the critical trials (i.e. direct-modification data) from the fifth pilot are included. 

``` {r}
pilot4 <- read_csv('../data/results_34_modXcongr_pilot1_tidy.csv') %>% 
  filter(adj_cond == "congruent") %>%
  mutate(pilot_nr = 4,
         syntax_dev = ifelse(syntax == "subj", 1, -1),
         syntax = ifelse(syntax == "subj", "subject", "predicate")) %>%
  select(-context_picture, -target_size, -adj_cond, -response_cat)
pilot5 <- read_csv('../data/results_35_modXrefUt_pilot1_nonMatchClassified_tidy.csv') %>% filter(trial_type == "critical") %>% 
  mutate(response_num = response_numMatch,
         pilot_nr = 5,
         syntax_dev = ifelse(syntax == "subj", 1, -1),
         syntax = ifelse(syntax == "subj", "subject", "predicate")) %>%
  select(-context_picture, -target_size, -adj_cond, -trial_type, -NP_match, -response_numMatch)

all5_pilots <- rbind(
  all_pilots %>% select(-response_cat, -response_label), 
  pilot4 ,
  pilot5
)
```

Full dataset plot by-syntax:
``` {r}
bar.width = 0.8

all5_pilots %>%
  group_by(syntax) %>%
  tidyboot_mean(column = response_num) -> all5_pilots.bs


all5_pilots.bs %>%
  ungroup() %>%
  mutate(syntax = factor(syntax, levels = c( "subject", "predicate"),
                            labels = c(  "Subject NP\n(That big NP is a prize-winner)", "Predicate NP\n(That prize-winner is a big NP)"))) %>%
  ggplot(., aes(x=syntax, y = mean, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(bar.width), width = bar.width, color= 'black',
           alpha = 0.5, color = 'black', size = 0.5) +
  geom_linerange(position = position_dodge(bar.width), size = 0.5) +
  ggthemes::theme_few()+
  xlab("") +
  theme(legend.position = c(0.88, 0.84),
        legend.key.size = unit(0.5,"line"))+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  ylab("Proportion of responses\n not matching NP") +
  ggtitle("E4 Direct Modification Pilots 1-5")

```

## Pilot 1-5 stats
``` {r}
all5_pilots <- all5_pilots %>%
  mutate(pilot_nr = factor(pilot_nr))

d.mod.full5.brm <- brm(response_num ~ syntax_dev + pilot_nr + 
                          (1 + syntax_dev | submission_id ) + 
                          (1 + syntax_dev | target ),
                   data = all5_pilots,
                   family = "bernoulli",
                   cores = 4,
                   control = list(adapt_delta = 0.99))

summary(d.mod.full5.brm)
```