--- 
title: "Comparison class inference free production 50 participants"
author: "Polina Tsvilodub"
date: "09/06/2019"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

```

``` {r}
library(tidyverse)
library(tidyboot)
library(brms)
library(lme4)
```

``` {r}
d1 <- read_csv("../data/results_12_comp-class-infer-pred.csv")
d2 <- read_csv("../data/results_13_comp-class-infer-prenom.csv")
d <- rbind(d1, d2)

glimpse(d)
```

``` {r}
# ref_spec: 0 os subordinate, 1 is basic label 
# picture: 0 is basic + congruent adjective, 1 is subordinate + congruent, 2 is subordinate + incongruent. 3 basic trials per subject and 3 randomly sampled adjective condition subordinate trials  
d <- mutate(d, NP = factor(ref_spec, levels= c(0, 1), labels = c("great dane", "one")), context_adj = factor(pic_spec, levels = c(0, 1, 2), labels = c("congruent dog parade", "congruent great dane parade", "incongruent great dane parade")))


```

``` {r}
d %>% distinct(d$languages) %>% View()
d_filt <- d %>% 
  filter(grepl("en", languages, ignore.case = T))

# comments
d_comments <- d_filt %>% select(comments, problems) %>% distinct()
# choose main trials 
d_main <- d_filt %>% filter((trial_name == "custom_main_text1")|(trial_name == "custom_main_text2")) %>% select(submission_id, trial_number, NP, context, context_adj, item, response, condition, context_picture, adj_cond, target_size)

d_main %>% distinct(d_main$response)  %>% View()
```
## Response categorization
```{r}
# remove invalid responses : no invalid responses!

# categorize responses
d_main_responseCat <- d_main %>%
  rowwise() %>%
  mutate(  
    response_cat =
      ifelse(
        tolower(response) %in% c("birds", "dogs", "fish", "fishes", "flowers", 
                                 "flower", "large dogs", "dogs in the line",
                                 "other birds in the group", "small dogs", "trees",
                                 "tree's", "bird", "big tree"), "basic", 
        ifelse(tolower(response) %in% c("plant", "animal", "things", "weeds", "plants"),
               "super", "sub")),
    
    response_num = ifelse(response_cat == "basic", 1, 0),
    response_label = "basic"
  )

```

``` {r}
# raw reponse counts by syntactic condition (6 participants each)
d_main_responseCat %>% ggplot(aes(x=response_cat)) + geom_bar(position=position_dodge()) + facet_wrap(~condition) 
```
## Include item frequencies 
``` {r}
item_freqs <- read_csv('../data/item_freqs.csv') 
# include the pure basic level category string
d_main_responseCat <- d_main_responseCat %>% rowwise() %>% mutate(basic_cat = ifelse(item == "dogs1", "dogs",
                                                ifelse(item == "dogs2", "dogs", item)))
# include the subordinate level category string 
                                                                                          ) ) )
return_item <- function(condition, context_pic, target_size) {
  if(condition == "incongr") {
    x = sub("images/.*-parade-", "", context_pic)
    x = sub(".png", "", x)
    x = sub("-", " ", x)
  } else if (condition == "congr") {
    x = sub("images/.*-parade-", "", context_pic)
    x = sub(".png", "", x)
    x = sub("-", " ", x)
  } else {
    if (context_pic == "images/bird-parade-basic.png") {
      if (target_size == "small") {
        x=  "hummingbird"
      } else {
        x= "eagle"
      }
    } else if (context_pic == "images/dog-parade-basic.png") {
      if (target_size == "small") {
        x= "chihuahua"
      } else {
        x= "doberman"
      }
    } else if (context_pic == "images/dog-parade-basic2.png") {
      if (target_size == "small") {
        x= "pug"
      } else {
        x= "great dane"
      }
    } else if (context_pic == "images/fish-parade-basic.png") {
      if (target_size == "small") {
        x= "goldfish"
      } else {
        x= "swordfish"
      }
    } else if (context_pic == "images/flower-parade-basic.png") {
      if (target_size == "small") {
        x= "dandelion"
      } else {
        x= "sunflower"
      }
    } else {
      if (target_size == "small") {
        x= "bonsai"
      } else{
        x= "redwood"
      }
    }
  }
  return(x) 
}
items_vec <- Vectorize(return_item, vectorize.args = c("condition", "context_pic", "target_size"))

exp_sub <- items_vec(d_main_responseCat$adj_cond, d_main_responseCat$context_picture, d_main_responseCat$target_size)

d_main_responseCat_w_freq$sub_freq <- item_freqs$log_sub_log_basic[match(d_main_responseCat_w_freq$exp_sub, item_freqs$np)]
d_main_responseCat_w_freq$basic_freq <- log(item_freqs$np_freqs[match(d_main_responseCat_w_freq$basic_cat, item_freqs$np)])
```

## Proportion of basic responses by syntactic condition, context specificity and NP 

Expectations: When the underspecified 'one' is used, participants infer the comparison class froom the perceptual context: subordinate label (comparison class) for the subordinate parade, basic-level label for the basic-level parade. When thue subordinate noun phrase is used, the prenominal syntax sets the comparison class, whereas the predicative syntax allows for stronger context influence: more basic-level labels in the basic-level context are expected than in the subordinate context. 

## Basic responses proportion by context condition
There might be confusion within participants in the 'one' condition, since it is potentially confusing if 'small one' refer to different things in the basic and incongruent subordinate condition. 
``` {r}
d_main_responseCat$condition <- factor(d_main_responseCat$condition, levels = c("prenominal", "predicative"))

d_main_responseCat %>% group_by(response_label, NP, context_adj, condition) %>%
  tidyboot_mean(column = response_num) %>% ungroup() %>% 
  mutate(condition = factor(condition, levels = c("prenominal", "predicative"), 
                            labels = c("That's a big NP", "That NP is big"))) %>%
  ggplot(aes(x=condition, y = mean, fill = NP, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(0.8)) +
  geom_linerange(position = position_dodge(0.8)) + 
  scale_fill_manual("NP", values = c("great dane" = "blue", "one" = "brown")) +
  xlab("syntactic condition") +
  ylab("proportion of basic-level responses")+
  facet_grid(~context_adj)  
```

``` {r}
# collpase the subordiante context picture conditions
d_main_responseCat <- d_main_responseCat %>% rowwise() %>% 
  mutate(context_cats = ifelse(context_adj == "congruent dog parade", 
                                      "Dog parade", "Great dane parade"))
d_main_responseCat$context_cats <- factor(d_main_responseCat$context_cats, 
                                          levels = c("Dog parade", "Great dane parade"))

d_main_responseCat %>% group_by(response_label, NP, context_cats, condition) %>%
  tidyboot_mean(column = response_num) %>% ungroup() %>% 
  mutate(condition = factor(condition, levels = c("prenominal", "predicative"), 
                            labels = c("That's a big NP", "That NP is big"))) %>%
  ggplot(aes(x=condition, y = mean, fill = NP, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(0.8)) +
  geom_linerange(position = position_dodge(0.8)) + 
  scale_fill_manual("NP", values = c("great dane" = "blue", "one" = "brown")) +
  facet_grid(~context_cats)  

```

``` {r}
d_basic_context <- d_main_responseCat %>% filter(context_cats == "Dog parade")
lm.basic <- lmer(response_num ~ condition * NP + (1|submission_id) + (1 + condition|item), data = d_basic_context, family = "binomial")
summary(lm.basic)
```

``` {r}
d_congruent <- d_main_responseCat %>% filter(context_adj == "congruent dog parade" | context_adj == "congruent great dane parade") %>% mutate(context_specs = context_adj)
# predicative reference level
contrasts(d_congruent$condition)=matrix(c(-1, 1))
# subordinate reference level
contrasts(d_congruent$NP)=matrix(c(-1,1))
# 
contrasts(d_congruent$context_specs)=matrix(c(-1,1,0))
blm.basic <- brm(response_num ~ 0 + condition * NP * context_adj + (1|submission_id) + (1 + condition|item), data = d_congruent, family = "binomial")
  summary(blm.basic)
```

``` {r}
# congruent vs incongruent trials
d_main_responseCat %>% group_by(adj_cond, response_label) %>% 
  tidyboot_mean(column = response_num) %>% ungroup() %>%
  ggplot(aes(x = adj_cond, y = mean, fill = adj_cond, 
             ymin = ci_lower, ymax = ci_upper)) + 
  geom_col(position = position_dodge()) +
  geom_linerange(position = position_dodge()) 
  
```

## Stats
``` {r}

lm.fit <- glmer(response_num ~ condition*NP*context_adj + (1|submission_id), 
                data = d_main_responseCat, family = "binomial" )
summary(lm.fit)
```

## Condition counts table 
``` {r}
d_main_responseCat %>% group_by(condition, NP, context_adj) %>% count()

```
## Basic responses proportion by item, target size and context
``` {r}
d_main_responseCat$condition <- factor(d_main_responseCat$condition, levels = c("prenominal", "predicative"))

d_main_responseCat %>% 
  group_by(item, condition, response_label, NP, context_adj, target_size) %>% 
  tidyboot_mean(column = response_num) %>% ungroup() %>%  
  ggplot(aes(x=condition, fill= NP, y = mean, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(0.8))+
  geom_linerange(position = position_dodge(0.8)) + 
  facet_grid(item*target_size~context_adj, space = "free_y") + coord_flip() +
  theme(strip.text.y = element_text(angle = 0)) + 
  scale_fill_manual("NP", values = c("great dane" = "blue", "one" = "brown")) # + ggsave("by_item.jpg", width = 15, height = 20, units= "in")
# flip right side labels to horizontal orientation, angle is relative to normal 

```

## Response consistency within participants
``` {r}
d_main_responseCat$condition <- factor(d_main_responseCat$condition, levels = c("prenominal", "predicative"))

d_main_responseCat %>%
  group_by(submission_id, condition, response_label, NP, context_adj) %>%
  summarize(n_basic_responses = sum(response_num)) %>%
  ungroup() %>% 
  ggplot(., aes( x = n_basic_responses, fill=NP)) +
  geom_bar(position=position_dodge()) +
  facet_grid(condition~context_adj) + 
  ggtitle("Number of basic responses uttered per participant in the 3 trials") +
  scale_fill_manual("NP", values = c("great dane" = "blue", "one" = "brown"))
```
## Size effects: Basic responses proportion by size 
``` {r}
d_main_responseCat$condition <- factor(d_main_responseCat$condition, levels = c("prenominal", "predicative"))

d_main_responseCat %>% group_by(response_label, NP, context_adj, condition, target_size) %>% tidyboot_mean(column = response_num) %>% ungroup() %>% 
  mutate(condition = factor(condition, levels = c("prenominal", "predicative"), 
                            labels = c("That's a big NP", "That NP is big"))) %>%
  ggplot(aes(x=condition, y = mean, fill = NP, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(0.8)) +  
  geom_linerange(position = position_dodge(0.8)) + 
  scale_fill_manual("NP", values = c("great dane" = "blue", "one" = "brown")) +
  facet_grid(target_size~context_adj)

```
## First trial analysis
```{r}
d_main_responseCat$condition <- factor(d_main_responseCat$condition, levels = c("prenominal", "predicative"))


# order effects 
d_main_responseCat %>% filter(trial_number == 1) %>% 
  group_by(response_label, NP, context_adj, condition) %>% 
  tidyboot_mean(column = response_num) %>% ungroup() %>% 
  mutate(condition = factor(condition, levels = c("prenominal", "predicative"), 
                            labels = c("That's a big NP", "That NP is big"))) %>%
  ggplot(aes(x=condition, y = mean, fill = NP, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(0.8)) +  
  geom_linerange(position = position_dodge(0.8)) + 
  scale_fill_manual("NP", values = c("great dane" = "blue", "one" = "brown")) +
  facet_grid(~context_adj)

```