---
title: "Comparison Class Inference Novel context pilot"
author: "Polina Tsvilodub"
date: "10 10 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libs, echo = FALSE}
library(tidyverse)
library(tidyboot)
library(lmerTest)
```

## Outline

In this pilot, in contrast to the previous comparison class inference free production experiment we only have congruent conditions. Furthermore, we included an third noun phrase condition (basic-level NP), to be more consistent with the other experiments. We now mention the subordinate category of the target referent in the context setup to provide the necessary information for the basic-level NP condition. An example trial would look like this: 
The first sentence is "You and your friend see the following:", Then a context picture is presented. Below, the sentence "You and your friend see another great dane ( not pictured ) and your friend says: " appears. The critical sentence could be "That is a big great dane."
30 participants (15 per syntactic condition) were recruited, no data points were excluded. 

__Between-subjects:__ syntactic condition (subject NP vs predicate NP)
__Within-subjects:__ Noun Phrase ('one' vs subordinate level vs basic-level label), context picture (basic-level vs subordinate parade)
__Expectation:__ Basic - level context: In the basic-level NP condition, we expect similarly high basic response proportions in both conditions. In the subordinate NP condition (critical condition), we expect an effect of syntax: less basic responses in the predicate NP than in the subject NP condition. In the 'one' condition we also expect similarly high basic response proportions across syntactic conditions.
Subordinate context: We might expect more basic responses in the basic Np condition than in the other two. We expect similarly high subordinate response proportions in the 'one' condition across syntactic conditions. In the subordinate NP condition, we might expect a smaller syntax effect than in the basic context condition  and an overall small basic response proportion. 

## Results

Including the subordinate label of the persumable target in the context setup seems to have an effect on the inferences in an unexpected way. 

1. Basic-level context: In the underspecified noun phrase condition ('one'), the reference of the NP is interpreted to be the subordinate category. We see an effect of the syntactic condition: there are less basic-level responses in the predicate NP condition than in the subject NP condition. 
2. In the subordinate noun phrase condition, we do not see any syntax effect, around 90% of responses are basic-level. This seems to indicate that both the predicate and the subject NP are interpreted referentially, to distinguish the target from the basic-level context. 
3. In the basic-level noun phrase condition, we see an overall lower proportion of basic-level responses than in the subordinate condition. There seems to be a tendency towards less basic-level responses in the predicate condition. However, there is a big variance, given the small sample size. 
4. Subordinate context: the results look very similar to the basic level condition, just with a lower overall basic response proportion. There might be a tendency to syntax sensitivity in the subordinate NP context, but the errors are very big. Again, we see a surprisingly high basic response proportion in the subordinate NP condition, indicating that the subordinate is interpreted referentially.  
```{r }
d1_infer <- read_csv("./../data/results_12_comp-class-infer-pred_congr.csv")
d2_infer <- read_csv("./../data/results_13_comp-class-infer-prenom_congr.csv")
d_infer <- rbind(d1_infer, d2_infer)

d_infer <- mutate(d_infer, NP = factor(ref_spec, levels= c(0, 1, 2), 
                                       labels = c("subordinate", '"one"', "basic")), 
                  context = factor(pic_spec, levels = c(0, 1), 
                                       labels = c("basic-level parade", 
                                                  "subordinate parade")))
d_infer_filt <- d_infer %>% 
  filter(grepl("en", languages, ignore.case = T))
# choose main trials 
# 2 (context) x 3 (NP) x 2 (condition)
d_infer_main <- d_infer_filt %>% filter((trial_name == "custom_main_text1")|
                                          (trial_name == "custom_main_text2")) %>%
  select(submission_id, trial_number, NP, context, item, response, condition,
         context_picture, target_size)

d_infer_main_responseCat <- d_infer_main %>%
  rowwise() %>%
  mutate(  
    response_cat =
      ifelse(
        tolower(response) %in% c("birds", "dogs", "fish", "flowers", 
                                 "flower", "trees", "dog breeds",
                                 "fishes", "dog", "Fish"), "basic", 
        ifelse(tolower(response) %in% c("things", "weeds", "plants"),
               "super", "sub")),
    
    response_num = ifelse(response_cat == "sub", 0, 1),
    response_label = "basic"
  )


d_infer_main_responseCat$condition <- factor(d_infer_main_responseCat$condition, 
                                             levels = c("prenominal", "predicative"))
bar.width = 0.8
d_infer_main_responseCat %>%  
  group_by(response_label, NP, context, condition) %>%
  tidyboot_mean(column = response_num) %>% ungroup() %>% 
  mutate(condition = factor(condition, levels = c( "predicative", "prenominal"), 
                            labels = c( "Subject", "Predicate"))) %>%
  ggplot(aes(x=condition, y = mean, fill = NP, ymin = ci_lower, ymax = ci_upper)) +
  geom_col(position = position_dodge(bar.width), width = bar.width) +
  geom_linerange(position = position_dodge(bar.width)) + 
  xlab("NP condition") +
  ylab("proportion of basic-level responses")+
  facet_grid(~context)  

```
## Conclusion

It is not entirely clear if the change in observed effects is due to the context manipulation or also due to the presence of the basic-level NP condition. 

## Stats
The coding has to be adjusted, since there is a three-level variable now.
``` {r}

# 1 prenominal, -1 predicative
d_infer_main_responseCat <- d_infer_main_responseCat %>% mutate(
  condition = ifelse(condition == 'predicative', -1, 1),
                                   NP_code = ifelse(NP == 'basic', -1/3, 1/3),
                                   context = ifelse(context == 'basic-level parade',
                                                         -1, 1))

```

``` {r lmer}
lm.fit <- glmer(response_num ~ condition*NP_code*context + 
                  (1 + condition*NP_code*context ||submission_id) + 
                  (1 + condition*NP_code*context ||item), 
                data = d_infer_main_responseCat, family = "binomial", REML = F)
summary(lm.fit)
```